\ProvidesFile{latexfileinfo_pkgs.tex}[2012/05/29 v0.22 latex file info packages (UL)] 
% \ProvidesFile{finfpkgs.tex}[2012/05/06 v0.2 latex file info packages (UL)] 
\head \charset{ISO-8859-1} %%% {utf-8} 
  \texrobots
  \title{Display LaTeX file metadata ("info")}
%   \stylesheet{all}{plain}                     %% tried 2012/05/06
  </head><body>\CLBrk %%% \body 
    \lineanc{top-of-page} %%% \textopofpage
\EXECUTE{\let\CPR\ctanpkgref \def\title{\heading1} \def\section{\heading2}
         \def\subsection{\heading3}                \let\pkg\pkgnamefmt
         \def\fakeitem{\bullet\enspace}
         \def\strongcs#1{\strong{\cs{#1}}} 
         \def\metaarg#1{\code{\{\metavar{#1}\}}}
}
% \EXECUTE{\BlogInterceptHash}        %% upfinfo.sh instead
% \EXECUTE{\RequirePackage{monofill}} %% upfinfo.sh instead
% \EXECUTE{\let\pkgnamefmt\code}
\title{\code{latexfileinfo-pkgs} ---\vspace{6} Displaying \Wikienref{Metadata} 
          (\endqtd{Info}) of \emph{\LaTeX} Source Files}

\pardash a comparison of packages available from \acro{CTAN}
% \small[\,\UseVersionOf{finfinfo.tex}~as~of~\UseDateOf{finfinfo.tex}\,]\endsmall
%% <- TODO \relax 2012/04/09
  <p>   %%% \vspace{24}
\begin{small}
[\,\ancrefslist{{{intro}{intro}}
                {{table}{table}}
                {{single}{\cs{GetFileInfo}~etc.}}
                {{several}{\cs{listfiles}~etc.}}{{rcs}{rcs/svn}}
                {{thanks}{thanks}}}\,]\quad 
[\,\textit{\fileref{\htmljob}{reload}}\,]
\end{small}
\nextruleview{intro}
\section{0\quad Introduction (with links to sections)}
For \Wikienref{\LaTeX} source files, 
it is recommended to start them with \LaTeX\ command 
\begin{itemize}
  \item \cs{ProvidesClass}\code{ ~}\quad (for \file{.cls} files)
  \item \cs{ProvidesPackage}\quad        (for \file{.sty} files)
  \item \cs{ProvidesFile}\code{ ~ }\quad (for all other   files)
\end{itemize}
(after \cs{NeedsTeXFormat}). 
Their trailing optional argument can provide the most recent 
\begin{itemize}
  \item \wikienref{Revision control}{revision} \strong{date}\\ 
        (expected as \emph{\endqtd{first word}} in trailing optional argument)
  \item the corresponding \strong{version} string\\
        (expected as \emph{\endqtd{second word}} 
         in trailing optional argument)\pardash and
  \item and a brief \strong{description} of the file ("caption")\\
        (expected as anything \emph{else} in trailing optional argument).
\end{itemize}
Here we are listing and comparing \TeX\ packages available from 
\httpref{ctan.org}{\acro{CTAN}} that make use of this information.
  <p>
The document especially describes five packages of my own, 
including interrelations and dependencies, and thus extends 
their documentations; see \ancref{table}{table below} for them. 
An \emph{asterisk}* near a package name indicates that the package 
is \emph{not mine}; so what I tell about it may be wrong or bad \dots\
(please let me know via \webdesignref{contact.html}{form}, 
 or should I add something?) ...
  <p> 
We have the \emph{cases} of     %% single vs. several
\begin{enumerate}
  \item displaying \ancref{single}{single} file info (\strongcs{GetFileInfo} ...)
  \item listing infos of \ancref{several}{several} files (\strongcs{listfiles} etc.)
\end{enumerate}
and for each                    %% LaTeX vs. external
\begin{enumerate-a}
  \item access by \emph{\LaTeX} (\ancref{sing-ltx}{1\,}\cdot\ancref{sev-ltx}{\,2})
  \item access by \emph{external} program (\ancref{sing-ext}{1\,}\cdot\ancref{sev-ext}{\,2}).
\end{enumerate-a}
\emph{Related} subjects are using 
\begin{enumerate-i}
  \item \ancref{rcs}{revision control systems} and
  \item modification time according to \ancref{filemod}{pdf\TeX}.
\end{enumerate-i}
\lineanc{table}A \emph{tabular overview} of the first two case distinctions: 
  <p> 
\begin{stdallrulestable}
    \endcell just using \emph{\LaTeX}\qquad \endcell using \emph{external} program 
  \endline
    \textbf{\ancref{single}{single} file}\endcell
      \fakeitem \ancref{doc}{\pkg{doc}}* ~ ~ ~ ~ ~ ~\,\,\,
                (Frank \ctanpkgauref{mittelbach}{Mittelbach})\\
      \fakeitem \ancref{zwgetfdate}{\pkg{zwgetfdate}}*\,\,\,\,\,\,\,\,
                (Zden\unicodehexentity{011b}k \ctanpkgauref{wagner}{Wagner})\\
      \fakeitem \ancref{readprov}{\pkg{readprov}}
    \endcell
      \fakeitem \ancref{lfv} {\pkg{latexfileversion}}* 
                \,(Harald \ctanpkgauref{harders}{Harders})    \\
      \fakeitem \ancref{lfi} {\pkg{ltxfileinfo}}*~ ~ ~ ~ \,\,\,\,\,\,\,\,\,
                \,(Wybo \ctanpkgauref{dekker}{Dekker})        \\
      \fakeitem \ancref{tofi}{\pkg{typeoutfileinfo}}
  \endline
    \textbf{file \ancref{several}{list}}\endcell
      \fakeitem \ancref{cl}  {\pkg{classlist}}*~~~~~~~\,\,\,\,
                (Heiko \ctanpkgauref{oberdiek}{Oberdiek})   \\
      \fakeitem \ancref{dl}  {\pkg{dateiliste}}*~~~~~ ~\,
                \,(Paul \ctanpkgauref{ebermann}{Ebermann})    \\
      \fakeitem \ancref{lnfl}{\pkg{longnamefilelist}}       \\
      \fakeitem \ancref{nfl} {\pkg{nicefilelist}}           \\
      \fakeitem \ancref{mfl} {\pkg{myfilist}}               \\
    \endcell
      \fakeitem[\ancref{ltxinput}{\pkg{ltxinput}}* ~ ~ ~ ~ ~ ~ ~ ~ \,\,\,\,\,\,
               (Jim \ctanpkgauref{green}{Green})]         \\
      \fakeitem[\ancref{tle}{\pkg{texlog-extract}}* ~ \,\,\,
               (Wybo \ctanpkgauref{dekker}{Dekker})]       \\
                                                            \\
      [\,don't really belong here \dots\,]                  \\
      \\
\end{stdallrulestable}

\nextruleview{single}
\section{1\quad Access Single File Info}
%% v0.11: distributing intro words over first two subsections
% \internallinksbar{{{sing-ltx}{a}}{{sing-ext}{b}}{{filemod}{c}}}
\begin{small}
  [\,\ancref{sing-ltx}{a:}\enspace 
     \ancrefslist{{{doc}{\pkg{doc}}}
                  {{readprov}{\pkg{readprov}}}
                  {{zwgetfdate}{\pkg{zwgetfdate}}}
                  }\,]\quad 
  [\,\ancref{sing-ext}{b:}\enspace
     \ancrefslist{{{lfv}{\pkg{latexfileversion}}}
                  {{lfi}{\pkg{ltxfileinfo}}}
                  {{tofi}{\pkg{typeoutfileinfo}}}}\,]\quad 
  [\,\ancref{filemod}{c:\enspace \pkg{filemod}}\,]
\end{small}
\subsection{\lineanc{sing-ltx}a.\quad Access in \emph{\LaTeX} Run}
%% shortening 2012/04/05:
\emdash originally for \emph{automatic} inclusion of \emph{current} 
revision date and version of a package %%% (? cf.~\ancref{sing-ext}{next subsection}) 
in \emph{typesetting} the latter's documentation
(\textit{\endqtd{This document describes version \dots\ as of \dots}}), but then \dots
\begin{description}
  \ditem{\lineanc{doc}\CPR{doc}*} 
    \begin{itemize}
      \item Belongs to \LaTeX\ \CtanPkgRef{latex-base}{base} distribution. 
      \item Provides \strong{\cs{GetFileInfo}}\code{\{\metavar{file}\}}; after using this, 
        you have \cs{filedate}, \cs{fileversion}, \cs{fileinfo} of \metavar{file}.
      \item \metavar{file} must have been \emph{loaded} in the \LaTeX\ run.
      \item \cs{GetFileInfo} is \emph{fragile}.
    \end{itemize}
  \ditem{\lineanc{zwgetfdate}\CPR{zwgetfdate}*} 
    \begin{itemize}
      \item Provides \strongcs{DateOfFile}\metaarg{file}
                 and \strong{\cs{DateOfPackage}}\metaarg{file}. 
      \item \metavar{file} must have been \emph{loaded}. 
    \end{itemize}
  \ditem{\lineanc{readprov}\CPR{readprov}}
    \begin{itemize}
      \item %%% \pkg{readprov} further provides %%% \emph{robust}, expandable 
        Provides
        \strongcs{UseDateOf}\metaarg{file} and \strongcs{UseVersionOf}\metaarg{file}
        \Endash \emph{robust} (expandable).                         %% add. 2012/05/29
      \item %%% It steals
%         Steals \ancref{doc}{\pkg{doc}}'s \strongcs{GetFileInfo} so \pkg{doc} is not 
%         needed, in case ...
        %% <- 2012/05/26 ->
        Provides \ancref{doc}{\pkg{doc}}'s \strongcs{GetFileInfo} 
        (with modified definition; used internally)                 %% was "useed" 2012/05/29
      \item Provides 
        \begin{itemize}
          \item \strongcs{ReadFileInfos}\metaarg{files}
          \item \strongcs{ReadPackageInfos}\metaarg{files}
          \item \strongcs{ReadClassInfo}\metaarg{file}
        \end{itemize}
        as \emph{alternatives} to \cs{GetFileInfo}. 
      \begin{itemize}                               %% 2012/04/05
        \item They do \emph{not} really \emph{load} \metavar{file}/\metavar{files} ...
        \item ... so can be used with incompatible packages and 
          classes (multiple latter by \cs{ReadFileInfos\{\metavar{base}.cls\}}). 
        \item This allows \strong{adding arbitrary} \LaTeX\ source files 
          to the list of files that \LaTeX\ manages for 
          \ancref{latex}{\strong{\cs{listfiles}}}\pardash this is used for 
          \ancref{myfilist}{\pkg{myfilist}}.
      \end{itemize}
    \end{itemize}
\end{description}
\subsection{\lineanc{sing-ext}b.\quad \emph{Screen} Display Using \emph{External} Program}
\emdash when you wonder whether the most recent version of a package 
or a chapter file is present \dots
\begin{description}
  \ditem{\lineanc{lfv}\CPR{latexfileversion}*} 
    \begin{itemize}
      \item \Wikienref{Bash (Unix shell)} script.
      \item \emph{Nice} screen display.             %% TODO sample  2012/05/05
      \item Invokes \code{latex} run using a copy of 
            \ancref{doc}{\pkg{doc}}'s \cs{GetFileInfo}. 
    \end{itemize}
  \ditem{\lineanc{lfi}\CPR{ltxfileinfo}*} 
    \begin{itemize}
      \item \Wikiendisambref{Ruby}{programming language} script.
      \item Displays nice 
        \mirrorctanref{support/ltxfileinfo/doc/ltxfileinfo.html}{table}
        of infos (including \emph{location} in file system) on screen.
    \end{itemize}
  \ditem{\lineanc{tofi}\CPR{typeoutfileinfo}} 
    \begin{itemize}
      \item 5-lines \Wikienref{Bash (Unix shell)} script.
      \item Expects \code{latex} won't append too many screen lines after 
            1-line \strongcs{typeout}\\ 
            (\emph{tolerable} screen display as compared with 
            \ancref{lfv}{latexfileversion}).
      \item Invokes \code{latex} run using \ancref{readprov}{\pkg{readprov}}.
    \end{itemize}
\end{description}
\subsection{\lineanc{filemod}c.\quad Related, while different ...}
\begin{description}
  \ditem{\CPR{filemod}*}
    \begin{itemize}
      \item Uses \tugref{applications/pdftex/NEWS}{\pdfTeX}'s 
            \cs{pdffilemoddate\{\metavar{file}\}} primitive.
      \item Compares modification dates of files.
      \item Files include images.
      \item Also works with \code{pdflatex} in \acro{DVI} mode.
    \end{itemize}
\end{description}

\nextruleview{several}
\section{2\quad File Info List}
This is about listing \emph{all} files input in a \LaTeX\ run, \emph{or}~...
\subsection{\lineanc{sev-ltx}a.\quad Create in \LaTeX\ Run}
\begin{small}
[\,\ancrefslist{{{latex}{\pkg{LaTeX}}}
                {{cl}{\pkg{classlist}}}
                {{dl}{\pkg{dateiliste}}}
                {{lnfl}{\pkg{longnamefilelist}}}
                {{mfl}{\pkg{myfilist}}}
                {{nfl}{\pkg{nicefilelist}}}}\,]
\end{small}
\begin{description}
  \ditem{\lineanc{latex}\CPR{latex}*}
    \begin{itemize}
      \item \LaTeX\ provides \strong{\cs{listfiles}} for the document preamble.
      \item \cs{listfiles} issues a list of \strong{all} files input in the \code{latex} run 
            near end of \file{.log} file, together with their infos according 
            to \cs{Provide...} commands.
      \item The list is a \strong{two-column} "table" (plain text), \emph{base} filenames
            flush right, \emph{info} (maybe date, maybe version, maybe anything) flush left.
      \item Any file whose base \Wikienref{filename} has \strong{more than 8}~characters 
            or whose filename extension does \emph{not} have 3~characters \strong{corrupts} alignment. 
    \end{itemize}
  \ditem{\lineanc{cl}\CPR{classlist}*}
    \begin{itemize}
      \item Remembers (separately) files input by ~(a)~\strong{\cs{documentclass}}~ 
        and what was input by ~(b)~\strong{\cs{LoadClass}}.
      \item On \strong{\cs{PrintClassList}}, the list of loaded class files appears on screen.
      \item Configurable by \strongcs{PrintClassListEntry} and \strongcs{PrintClassListTitle}.
    \end{itemize}
  \ditem{\lineanc{dl}\CPR{dateiliste}*}
    \begin{itemize}
      \item Lists anything that the \ancref{latex}{original} \cs{listfiles} would list.
      \item \strong{Typesets} the list as a \LaTeX\ table, using package \CPR{longtable}. 
      \item Separate \strong{columns} for 
        \begin{itemize}
          \item filename
          \item \emph{page} where input (optionally)    %% \emph 2012/04/09
          \item date
          \item version
          \item description ("caption")
        \end{itemize}
      \item Supports \strong{\acro{RCS}}, 
          \wikienref{Concurrent Versions System}{\acro{CVS}}, 
          and \acro{SVN} (cf.~\ancref{rcs}{section below}).
      \item Highly configurable.
      \item E.g., you can replace info for a file by what you want to see in the list 
            (cf.~\ancref{myfilist}{\pkg{myfilist}}).
      \item I haven't seen what happens with \emph{plain text} (\file{.log}) output.
    \end{itemize}
  \ditem{\lineanc{lnfl}\CPR{longnamefilelist}}
    \begin{itemize}
      \item Overcomes \ancref{latex}{\LaTeX}'s "8-character~limit"
            by a new \strong{optional argument} for \cs{listfiles}, 
            indicating number of characters to be reserved for 
            base filenames, e.g. accounting for "\code{longnamefilelist.sty}": 
          \begin{quote}
            \cs{listfiles[16]}
          \end{quote}
            \pardash view
            \mirrorctanref{macros/latex/contrib/longnamefilelist/%
                SrcFILEs.txt}{example outcome} 
      \item \emdash showing combination with \ancref{mfl}{\pkg{myfilist}}
      \item \emdash while also working as single addition to 
            \LaTeX~\CtanPkgRef{latex-base}{base}, 
            \emph{no} need of \ancref{mfl}{\pkg{myfilist}} or \CPR{monofill}.
      \item Still, filename \strong{extension}s with number of characters 
            differing from 3 break alignment. Martin MÅnch mentions 
            \file{t1cmtt.fd} (standard \LaTeX\ font definition) and 
            \file{supp-pdf.mkii} (\Wikienref{ConTeXt}).
    \end{itemize}
  \ditem{\lineanc{nfl}\CPR{nicefilelist}}
    \begin{itemize}
      \item Uses separate \strong{columns} for \strong{date} and \strong{time} 
            (like \ancref{dl}{\pkg{dateiliste}}).
      \item (Picky) recognition of "date" and "version"\pardash if not present, 
            left \strong{empty} or gets "missing" display: 
          \begin{codelines}
            nicefilelist.sty~ 2012/03/29~ v0.2 ~ more file list alignment (UL)\/
            nicefilelist.tex~ 2012/03/23~ ~--~ ~ documenting nicefilelist.sty
          \end{codelines}
            (Martin MÅnch's idea).
      \item Problem of varying filename \strong{extension} lengths overcome 
            by actually keeping a separate flush-left column for them. 
      \item Column widths configurable by \strong{templates}\pardash replace
            pre-configuration (\CPR{monofill} commands):
          \begin{codelines}
            \EXECUTE{\MFfieldtemplate[~]{nfl}{%
                        /MFfieldtemplate(f-base)...(nicefilelist)..}}
            \MFleftinfield{%
              \\MFfieldtemplate\{f-base\}~~~\{nicefilelist\}}{nfl}\%\%\ base name \/
            \MFleftinfield{%
              \\MFfieldtemplate\{f-ext\}~~~~\{tex\}}{nfl}\%\%\     name extension \/
            \MFleftinfield{%
              \\MFfieldtemplate\{f-version\}\{v0.11a\}}{nfl}\%\%\       version
          \end{codelines}
      \item First code line above shows \strong{difference} to \CPR{longnamefilelist}, 
            equivalent there would be \cs{listfiles[12]}. 
            \pkg{nicefilelist} does \emph{not} provide an optional argument 
            for \cs{listfiles}.
      \item Column \strong{distances} and "\strong{missing}" display configurable too.
      \item Can be combined with \ancref{mfl}{\pkg{myfilist}}\pardash view
            \mirrorctanref{macros/latex/contrib/nicefilelist/%
                doc/%                                           %% 2012/05/26
                SrcFILEs.txt}{output sample}.
      \item Needs just \CPR{monofill}, additionally to 
            \LaTeX~\CtanPkgRef{latex-base}{base}.
      %% 2012/05/27:
      \item \pkg{nicefilelist} v0.4 provides an option \code{[r]} to allow 
            "release numbers" in the column reserved for versions:
          \begin{codelines}
            nicefilelist.sty~ 2012/05/20~ v0.4 ~ more file list alignment (UL)\/
            nicefilelist.tex~ 2012/05/20~ ~--~ ~ documenting nicefilelist.sty\/
            nicefilelist.RLS~ 2012/05/20~ r0.4 ~ v0.4 Kabelschacht + [r]
          \end{codelines}
            \file{.RLS} files are an idea to provide/access a release summary.
    \end{itemize}
  \ditem{\lineanc{mfl}\lineanc{myfilist}\CPR{myfilist}}
    \begin{itemize}
      \item Allows \strong{removing} all entries that \LaTeX\ has collected
            for \ancref{latex}{\cs{listfiles}} at a certain point 
            (\strong{\cs{EmptyFileList}}).                                  %% 2012/05/26
      \item Then, by commands from \ancref{readprov}{\pkg{readprov}}, 
            you can \strong{add arbitrary} files to the list 
            (as they are \emph{not} really \emph{loaded}), 
            in the order you want to have them in the list.
            %% 2012/05/29:
            (However, for many combinations of package files, 
             you could actually \emph{load} them, without \pkg{readprov}.)
      \item Thus actually, you can set up a list of files you want to have 
            \emph{independently} of a typesetting run ...
      \item ... and actually, the \strong{intended} application is generating the 
            list \strong{without} any \strong{typesetting}, 
            by running \code{latex} on a "\strong{script}" file 
            just loading \pkg{readprov} and \pkg{myfilist} 
            and using only commands from \emph{them}. 
            (No \cs{documentclass}, no \code{\{document\}} environment.)
      \item View 
            \mirrorctanref{macros/latex/contrib/longnamefilelist/docsrc/%
                srcfiles.tex}{input example} 
            for \ancref{lnfl}{\pkg{longnamefilelist}}.
      \item Besides \file{.log} output, the list can be written into a \strong{separate} 
            plain text \strong{file%%% } ...
%       \item ... view 
            }\pardash view
            \mirrorctanref{macros/latex/contrib/longnamefilelist/%
                SrcFILEs.txt}{output example} 
            for \ancref{lnfl}{\pkg{longnamefilelist}}.
      \item \strong{Main applications} in my mind and actual work:
        \begin{enumerate}
          \item List of \file{.sty} and \file{.tex} files for \emph{my} 
            \strong{\acro{CTAN} packages} and \strong{bundles}
            (instead of the \file{.dtx}/\CPR{docstrip} system, I use \CPR{nicetext}). 
          \item List of \strong{package} files specific to some \strong{project}
            that often change\pardash manual replacement for a 
            "concurrent versions" system with single author. 
            E.g.: 
            \begin{itemize}
              \item \CPR{nicetext} packages underlying \strong{documentation} 
                    of a certain different package.
              \item \strong{style} files underlying a \strong{book} project 
                    at which authors and programmers work on changing computers.
            \end{itemize}
          \item List of \strong{chapter} \cs{include} files for a \strong{book} project,
                edited at changing computers (by a number of authors).
          \item Often, one \strong{forgets} to \strong{update} version information 
                in the \cs{Provides...} command\pardash the \pkg{myfilist} 
                helps you to \pkg{check} this 
                (e.g., right before a release; 
                 \ancref{filemod}{\pkg{filemod}} might automate this check, 
                 perhaps together with \ancref{readprov}{\pkg{readprov}}, 
                 \emph{without} \pkg{myfilist}).
        \end{enumerate}
      \item My actual \strong{workflow} with \Wikienref{Bash (Unix shell)}:
        \begin{itemize}
          \item \strong{\code{upsfl}} with
            \begin{codelines}
                alias upsfl='latex srcfiles'} 
            \end{codelines}
            updates the list of source files, 
            and actually displays the updated list on screen.
          \item \strong{\code{shsfl}} with
            \begin{codelines}
                \code{alias shsfl='more SrcFILEs.txt'} 
            \end{codelines}
            displays the source file list without updating, 
            and waits when the list is too long for your (netbook) screen.
        \end{itemize}
      \item Combinable with \ancref{dl}{\pkg{dateiliste}}?
    \end{itemize}
\end{description}
\subsection{\lineanc{sev-ext}b.\quad Create by External Program}
Hm, not so related, \emph{no} infos (it seems), lists only; 
so, just \emph{"most related I could find"} for this section~...
\begin{description}
  \ditem{\lineanc{ltxinput}\CPR{ltxinput}*}
    \begin{itemize}
      \item \wikienref{MS-DOS}{\acro{MS-DOS}} utility 
            (compiled from \wikienref{C (programming language)}{\acro{C}}).
      \item Lists files that \emph{would} be input (recursively).
    \end{itemize}
  \ditem{\lineanc{tle}\CPR{texlog-extract}*}
    \begin{itemize}
      \item \Wikiendisambref{Ruby}{programming language} script.
      \item Lists files that issued errors and warnings (colored).
    \end{itemize}
\end{description}

\nextruleview{rcs}
\section{\lineanc{rcs}3\quad \acro{RCS}/\acro{SVN}}
For \wikienref{Revision control}{revision control systems} 
\wikienref{Revision control system}{\acro{RCS}} and 
\wikienref{Apache Subversion}{\acro{SVN}}, there are
\begin{itemize}
  \item \CPR{rcs}* \cdot\ \CPR{rcsinfo}* \cdot\ \CPR{rcs-multi}*
  \item \CPR{svn}* \cdot\ \CPR{svninfo}* \cdot\ \CPR{svn-multi}*
  \item \CPR{svn-prov}* provides \acro{SVN} variants of 
    \cs{ProvidesClass}, \cs{ProvidesFile}, and \cs{ProvidesPackage}. 
\end{itemize}
\emdash sorry, I can't tell more about them right now~\dots     %% 2012/04/08

\nextruleview{thanks}
\section{Acknowledgements}
Thanks to Martin MÅnch, Moss 
(I wrote this for his question),                %% 2012/04/06
and Rainer Schîpf!
\ancref{rcs}{\acro{RCS} stuff} mainly has been stolen from
\bytopicref{revision}{JÅrgen Fenn's Topic Index} of the 
\mirrorctanref{help/Catalogue}{\TeX~Catalogue}.
  <p>   %%% \vspace{24}
\hrule
\small*~not~mine\endsmall
\rightpar{\textit{%
    Last~revised~\isotoday\ \copyright~\webdesignref{contact.html}{Uwe LÅck}
    \vspace{6} 
    (using \CtanPkgRef{morehype}{blog.sty} 
     and   \CtanPkgRef{monofill}{monofill.sty}) 
    \vspace{6}
    License: \httpref{www.latex-project.org/lppl/}{LPPL~1.3c} or later, author-maintained.}}
\entotopofpage
\vspace{550}
\finish

%% HISTORY:
%% 2012/04/02   v0.1   first upload
%% 2012/04/02   v0.11  little improvements afterwards, 
%%                     especially intro words for section 1
%% 2012/04/05   v0.12  less words in section 1; 
%%                     sub-itemize for readprov
%% 2012/04/06          wrote for Moss
%% 2012/04/08          started table, some other additions
%% 2012/04/09          continued (fix of strange bug!?)
%% 
%% 2012/05/05f. v0.2   renamed `latexfileinfo-pkgs', table 
%%                     reformatted manually, minor rewordings
%%                     and reformattings, link fixes
%% 2012/05/13   v0.2a  modified \ProvidesFile for different 
%%                     generation method
%% 2012/05/26   v0.21  corr. \GetFileInfo, 
%%                     nicefilelist sample link fixed
%% 2012/05/27          nicefilelist's option [r]
%% 2012/05/29   v0.22  remark `myfilist' without `readprov', 
%%                     typo fix, \UseDateOf ... robust
