\NeedsTeXFormat{LaTeX2e}
\ProvidesFile{tools.tex}[2014/04/30 Tools overview (HO)]
% Copyright 2006-2014 Heiko Oberdiek
%
% This file is part of project `latex-tds'.
%
% It may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
%  http://www.latex-project.org/lppl.txt
% and version 1.3c or later is part of all distributions of LaTeX
% version 2005/12/01 or later.
%
% This work has the LPPL maintenance status `maintained'.
%
% The Current Maintainer of this work is Heiko Oberdiek.
%
% See `README' for a list of all files belonging to the
% project `latex-tds' and additional information.
%
\documentclass{tools-overview}
\begin{document}
\entry{afterpage}{%
  Place text after the current page.
}%
\entry{array}{%
  Extended versions of the environments array, tabular and tabular*.
}%
\entry{bm}{%
  Access bold math symbols.
}%
\entry{calc}{%
  Infix arithmetic expresions. Contributed to the distribution by
  Kresten Krab Thorup and Frank Jensen.
}%
\entry{dcolumn}{%
  Alignment on \emph{decimal points} in tabular entries. Requires array.
}%
\entry{delarray}{%
  Adds \emph{large delimiters} around arrays. Requires array.
}%
\entry{enumerate}{%
  Extended version of the enumerate environment.
}%
\entry{fileerr}{%
  Suite of small files which may be used to control \TeX{}'s
  missing file error loop.
}%
\entry{fontsmpl}{%
  Package and test file for producing \emph{font samples}
}%
\entry{ftnright}{%
  Place footnotes in the right hand column in two-column mode.
}%
\entry{hhline}{%
  Finer control over horizontal rules in tables. Requires array.
}%
\entry{indentfirst}{%
  Indent the first paragraph of sections etc.
}%
\entry{layout}{%
  Produces an overview of the layout of the current document.
}%
\entry{longtable}{%
  Multipage tables. (Does not require array, but uses the extended
  features if both are loaded.)
}%
\entry{multicol}{%
  Typeset text in columns, with the length of the final columns
  \emph{balanced}.
}%
\entry{rawfonts}{%
  Preload fonts under the old internal font names of \LaTeX{}2.09.
  Not recomended for new packages, but may help when updating old
  files.
}%
\entry{showkeys}{%
  Draft mode showing the \emph{keys} used by \cs{label}, \cs{ref}, \cs{cite} etc.
}%
\entry{somedefs}{%
  Selective handling of package options. (Used in rawfonts.sty.)
}%
\entry{tabularx}{%
  Defines tabularx environment (similar to tabular*) but modifies
  column widths, not inter-column space, to achieve a desired
  table width.
}%
\entry{theorem}{%
  Flexible definition of \emph{theorem-like} environments.
}%
\entry{trace}{%
  The package helps to suppress and to control the amount of tracing
  output (\cs{tracingall}) by taming calc and making NFSS less noisy.
}%
\entry{varioref}{%
  \emph{Smart} handling of page references.
}%
\entry{verbatim}{%
  Flexible version of verbatim environment.
}%
\entry{xr}{%
  eXternall References. Extend \cs{ref} to access \cs{label} commands in
  other documents.
}%
\entry{xspace}{%
  Smart space command that avoids the common mistake of missing
  spaces after command names.
}%
\end{document}
